PM Mungbean meta-analysis

### 2020-07-07 02_Preliminary_analysis.Rmd
Draft inspection/plot of FAOSTAT data for dry bean (mungbeans) production in australia

>>>>

```{r}
beans <- read.csv(here("data/FAOSTAT_data_7-6-2020.csv"))

glimpse(beans)

beans %>%
   filter(Item == "Beans, dry",
          Element == "Area harvested")%>%
   select(Year,Value)
   ggplot(aes(y = Value, x = Year))+
   geom_point()+
   geom_smooth()

beans %>%
   filter(Item == "Beans, dry",
          Element == "Yield")%>%
   ggplot(aes(y = Value *0.1, x = Year))+
   geom_point()+
   geom_smooth()

beans %>%
   filter(Item == "Beans, dry",
          Element == "Production")%>%
   ggplot(aes(y = Value, x = Year))+
   geom_point()+
   geom_smooth(method = "lm")
